|

### 2023-05-10 manuscript/Chapter2-appendix1.Rmd
update appendix1

Update the plot legend to tell what is the *greatest increase*

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise. The predators' hunting success (i.e. the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Each fitted curve represents an individual predator. (A) Individuals with the greatest increase in hunting success with experience (B) Individuals with the greatest decrease in hunting success with experience."}

>>>>

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise. The predators' hunting success (i.e. the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Each fitted curve represents an individual predator. (A) Individuals with a >0.5 change in hunting success with experience (B) Individuals with a <-0.5 change in hunting success with experience. (C) Individuals with a change in hunting success between -0.5 and 0.5"}
